Informal explination of study ``Ecotype detection in (geometric) morphometric data''

### 2013-01-10 documents/faqs_intro.Rnw
started using additional datasets from packages
beginning tables

<<source-scripts, results = 'hide'>>=
source('../src/fish_plotting.r')
@

@@

<<pls-fits, eval = FALSE>>=
gg.means
@
\begin{figure}[p]
  \centering
  \includegraphics{figure/pls-fits3}
  \caption{<+caption text+>}
  \label{fig:fish-fit}
\end{figure}

<<pca-plots, eval = FALSE>>=
gg.pca
@
\begin{figure}[p]
  \centering
  \includegraphics{figure/pca-plots3}
  \caption{<+caption text+>}
  \label{fig:fish-pca}
\end{figure}

@@

>>>>

<<source-scripts, results = 'hide'>>=
source('../src/fish_plotting.r')
source('../src/misc_data_plotting.r')
@

@@

<<pls-fits, eval = FALSE>>=
gg.means
@
\begin{figure}[p]
  \centering
  \includegraphics{figure/pls-fits3}
  \caption{Procrustes fit landmark dispersion for all taxa in comparison to mean landmark position in red.}
  \label{fig:fish-fit}
\end{figure}

<<pca-plots, eval = FALSE>>=
gg.pca
@
\begin{figure}[p]
  \centering
  \includegraphics{figure/pca-plots3}
  \caption{Comparison of first four pricipal components of Procrustes fit landmarks. Familes are highlighted.}
  \label{fig:fish-pca}
\end{figure}

@@

% model selection table
<<fish-model-table>>=
print(ftab, 
      table.placement = 'p',
      caption.placement = 'bottom',
      sanitize.text.function = function(x) x,
      sanitize.colnames.function = function(x) x)
@

<<fish-confusion>>=
print(fconf,
      table.placement = 'p',
      caption.placement = 'bottom')
@

<<logistic-plots, eval = FALSE>>=
gf
@
\begin{figure}[p]
  \centering
  \includegraphics{figure/logistic-plots}
  \caption{Relative probabilities of Characiform family identification from the first two principal components of shape. The first two pricipal components are plotted here because they are the predictors of family from the AICc-best model.}
  \label{fig:fish-logistic}
\end{figure}
